\documentclass[10pt]{report}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{url}

% global commands

\newcommand{\javalst}[2]{
  \lstset{language=Java,captionpos=b,tabsize=4,frame=single,numbers=left,
    numberstyle=\tiny,numbersep=10pt,breaklines=true,showstringspaces=false,
    basicstyle=\footnotesize,emph={label}, caption={#1}, label={#2}}
}
\newcommand{\initlisting}[2]{
  \lstset{language={#1},captionpos=b,tabsize=4,frame=single,numbers=left,
    numberstyle=\tiny,numbersep=10pt,breaklines=true,showstringspaces=false,
    basicstyle=\footnotesize,emph={label}, caption={#2}}
}

\newcommand{\nm}{{\bf proTrade}}
\newcommand{\nmsp}{{\nm \ }}
% end commands
\setlength{\parskip}{0.3cm}
\setlength{\parindent}{0cm}

\begin{document}

\title{\nmsp - A Professional Tennis Trading Environment}

\author{Corina Ciobanu \and Iskander Orazbekov \and Mir Sahin \and Paul Grigoras \and Radu Baltean-Lugojan}

\date{\today}         % inserts today's date

\maketitle            % generates the title from the data above

\begin{abstract}
Tennis trading is a steadily growing market on the Betfair Exchange, with more than 70\% of bets being placed in-play. In order to maintain market liquidity, exchanges must attract customers for example, by supplying them with better tools. By providing more information and better visualization techniques such a tool can help the trader improve his understanding and predict the market evolution, which should (potentially) lead to an increased profit.

In the case of tennis trading, the information required to understand and predict the evolution of the market associated with a particular match consists of the live score, player statistics, potentially a live video feed and - of course - the market data (evolution of betting odds). Ideally, this information is desired for both historical and live matches.

At the moment, no application provides the entire information. A number of solutions exist which allow visualization of historical market data, but they generally lack the more specific, tennis related data. For example the Fracsoft Data Viewer (\cite{site-fracsoft}) does not correlate market data with match data (scores, player statistics). BetAngel (\cite{site-betangel}) provides some tennis related data and prediction, but relies on the user to input the current match score by pushing buttons. This not entirely suited for the high rate with which data is updated. Ideally all the information should be automatically provided to the user to increase update speed and enhance usability.

\nmsp means to fill this gap, by providing all the information, betting and prediction functionalities for both historical and live matches, in an entirely automated fashion.

\end{abstract}

\tableofcontents

\chapter{Introduction}

\section{Importance of Tennis Trading}

This section explains why tennis trading is important, providing background information on the game itself but also on betting and trading.

\subsection{The Game of Tennis}

Many points, short points $\Rightarrow$ high market volatility, ideal for trading.

\subsection{Tennis Trading}

Exploits the high market volatility.

A lot of money bet on tennis games (e.g. 40 mil for us open final etc.).

A lot of money bet in-play.

\section{State of the Art Applications for Tennis Trading}

Although, as we have seen, tennis trading is a major market there are currently no good applications to support it.
Explain why, give examples.

\section{Our Solution}

\nmsp aims to fill this gap by providing ... (Briefly describe functionality, explaining why our application solves the issues $\rightarrow$ answering ``Why should you buy this product?'')

\chapter{Technical Description}

This chapter introduces the main technologies used in building the product, gives a high lelve overview of the application's design and describes some of the main technical challenges and how they were overcome.

\section{Technologies}
In order to deliver the responsive and rich application described in section ***, we have used a number of technologies/frameworks etc.:
\begin{description}
\item[SWT] Brief description
\item[SWTChart] Brief description 
\item[BetfairAPI] Brief description
\item[And so on] and so on
\end{description}

Our choice of technologies is explained in more detail in section ***.

\section{Design}
Explain the design of the software (high-level), possibly including a diagram of the major components of the project.

The diagram can be similar to the one on the slides, but should contain more technical information (not too much).

\section{Achievements/Results}
This section briefly looks at the main achievements and results of the project.
e.g. We delivered an application which does this and that (possible a screenshot could be included).

\chapter{Software Engineering Issues}

This chapter discusses how important aspects of Software Engieering were tackled.

\section{Choice of Technology}
What technology was used and why? What other technology was considered but not used and why?

(Here we look at the technology options - e.g. SWT vs Swing - and explain our choices.)

\section{Technical Challenges}
Any technical challenges encountered and how addressed?

\section{Risks}
Any risks anticipated, and how mitigated?

\section{Collaboration}
Any collaboration/coordination difficulties encountered and how addressed 

\section{Development Methodologies}
Methods \& Tools

\section{Testing}
Methods \& Tools

\section{Comparison of Plans with Actual Achievements }

\section{Effort}
Present estimates of length of code in each of the components, or any other comparable measure of the effort required.

\section{Contributions}
Summary of each team member's contributions 


\chapter{Validation}
Describes user validation \& testing methods in more detail.
Details of feedback from various groups.

\chapter{Conclusions}
  \begin{itemize} 
  \item Was the project successful?
  \item What did you learn?
  \item What might you have done differently?
  \end{itemize}  

\begin{thebibliography}{9}
\bibitem{bk-testing}
  Steeve Freeman, Nat Pryce,
  \emph{Growing Object-Oriented Software, Guided by Tests}, Addison-Wesley 2010

\bibitem{web-cyccom}
  Robert Chatley's course on Software Engineering Methods
  \url{http://en.wikipedia.org/wiki/Cyclomatic_complexity},
  Imperial College London

\bibitem{bk-aglsam}
  Jonathan Rasmusson,
  \emph{The Agile Samurai},
  Pragmatic Bookshelf,
  October 2010.

\bibitem{bk-aglflh}
  Jeff Langr and Tim Ottinger,
  \emph{Agile in a Flash},
  Pragmatic Bookshelf, 
  January 2011.

\bibitem{web-rbc}
  Robert Chatley's course on Software Engineering Methods
  \url{http://www.doc.ic.ac.uk/~rbc/302/},
  Imperial College London

\bibitem{site-fracsoft}
  Site of Fracsoft, authors of Fracsoft Data Viewer
  \url{http://www.fracsoft.com}

\bibitem{site-betangel}
  Site of BetAngel
  \url{http://www.betangel.com}
  
\bibitem{wiki-swt}
  SWT - Wikipedia
  \url{http://en.wikipedia.org/wiki/Standard_Widget_Toolkit}

\end{thebibliography}

\clearpage
\appendix

\chapter{Tennis Rules}

Brief overview of the tennis scoring rules.

\chapter{About Betting Odds and Tennis Trading}

Brief overview of betting and tennis trading.
Provide an example of trading.

\chapter{User guide}

\section{Installation Instructions}

\section{Quick Start Guide}

\section{FAQ}

\chapter{Exstensive Design}

\chapter{Testing}

\chapter{Statistics}

\chapter{Worklogs}

\end{document}

